Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-11 WSSSPE3/report/wg_appendix_user_community.tex
making Ethan's changes

POC:
Dan Gunter <dkgunter@lbl.gov> and 
Ethan Davis <edavis@lbl.gov>

@@

With a small amount of seed funding, it is possible that members of this group or other parties could
spend the time necessary to devise a survey of existing projects and deploy this, probably including traveli to
meetings and workshops for the various software communities.

>>>>

POC:
Dan Gunter <dkgunter@lbl.gov> and 
Ethan Davis <edavis@ucar.edu>

@@

With a small amount of seed funding, it is possible that members of this group or other parties could
spend the time necessary to devise a survey of existing projects and deploy this, probably including travel to
meetings and workshops for the various software communities.
